Towards a Cognitive System That Can Recognize Spatial Regions Based on Context

### 2012-01-25 code/scenarios/cdsr/trunk/papers/AAAI2012/main-aaai12-cdsr.tex
minor edits page 2

Dora's metric map is a collection of lines in a 2D global coordinate frame. Two example maps are pictured in Figure~\ref{fig:rooms}. These lines are generated by a process which uses input from the robot's odometry and laser scanner to perform simultaneous localization and mapping (SLAM). Lines in this SLAM map represent features extracted from laser scans wherever a straight line is present for long enough to be considered permanent. In practice, lines are generated at the positions of walls and any other objects that are flat at the height of the laser (e.g. bins, closed doors etc.). The robot's location in the metric layer is represented as a 2D position plus an orientation.

@@

To enable us to generate a range of different evaluation situations in a reasonable length of time, we have generated data from Dora in both real rooms and in simulation. Simulation is performed using the Player/Stage hardware abstraction layer~\cite{GerkeyVaughanHoward03} allowing us to run the system \emph{mostly unchanged} in a pre-defined environment. Also, to enable us to detect a wider range of objects than is usually possible (from armchairs to whiteboards), we used a simulated object recogniser in all runs. The recogniser was configured with types and positions of objects in the environment and was guaranteed to detected them when the robot was orientated towards them. This eliminated any errors from the recognition process, but was still influenced by errors in robot localisation.

>>>>

Dora's metric map is a collection of lines in a 2D global coordinate frame. Two example maps are pictured in Figure~\ref{fig:rooms}. Map lines are generated by a process which uses input from the robot's odometry and laser scanner to perform simultaneous localization and mapping (SLAM). Lines in this SLAM map represent features extracted from laser scans wherever a straight line is present for long enough to be considered permanent. In practice, lines are generated at the positions of walls and any other objects that are flat at the height of the laser (e.g. bins, closed doors etc.). The robot's location in the metric layer is represented as a 2D position plus an orientation.

@@

To enable us to generate a range of different evaluation situations in a reasonable length of time, we have generated data from Dora in both real rooms and in simulation. Simulation is performed using the Player/Stage hardware abstraction layer~\cite{GerkeyVaughanHoward03} allowing us to run the system mostly unchanged in a pre-defined environment. Also, to enable us to detect a wider range of objects than is usually possible (from armchairs to whiteboards), we used a simulated object recogniser in all runs. The recogniser was configured with types and positions of objects in the environment and was guaranteed to detect them when the robot was orientated towards them. This eliminated any errors from the recognition process, but was still influenced by errors in robot localisation.
